Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
update

Depression is not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021). These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020). While various studies have explored the impact of the pandemic on mental health, there remains a significant gap in understanding the nuanced interactions between socio-cultural factors and the prevalence of anxiety and depressive disorders during this period (Pfefferbaum & North, 2020).

@@

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

### Population subgroup by age
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-ageandtrend-graph
#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age in US"

# Load necessary libraries
library(tidyverse)
library(lubridate)
library(here)
library(ggplot2)
library(gridExtra)

@@

# Plotting the line graph
ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

### Population subgroup by race
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-raceandtrend-graph
#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Race and Ethnicity in US"

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Race_subgroup_trends.csv"))

### Population subgroup by education
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sexandtrend-graph
#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Sex in US"

>>>>

Depression and anxiety are not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021). These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020). While various studies have explored the impact of the pandemic on mental health, there remains a significant gap in understanding the nuanced interactions between socio-cultural factors and the prevalence of anxiety and depressive disorders during this period (Pfefferbaum & North, 2020).

@@

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

### Population subgroup by age

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-ageandtrend-graph
#| fig-cap: "Depressive Disorder Trend by Population Subgroup"

# Load necessary libraries
library(tidyverse)
library(lubridate)
library(here)
library(ggrepel)  # For better label placement
library(dplyr)

@@

# Define the specific date for placing the labels
mid_date <- as.Date("2024-03-04")

# Filter the data to get the rows for the specific date
mid_date_data <- data %>%
  filter(Date == mid_date)

# Plotting the line graph
p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
  labs(x = "Date", y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",  # Remove the separate legend
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

# Add labels to the lines with smaller font size
p + geom_text_repel(
  data = mid_date_data,
  aes(label = Subgroup),
  nudge_x = 0,  # Adjust this value based on your date range and aesthetics
  nudge_y = 0,
  direction = "y",
  size = 3  # Adjust the size of the labels here; smaller values mean smaller text
)

@@
